---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(janitor)
library(prob)
library(gtools)
```
#MVP

```{r}
titanic <- read_csv(here::here("data/titanic.csv"))
```

```{r}
titanic %>% 
  distinct(class)
```

```{r}
titanic_staff_notstaff <- titanic %>% 
  mutate(class = case_when(
    str_detect(class, "[0-9]+") ~ "passenger",
    TRUE ~ "staff"
  ))
```

```{r}
titanic_staff_notstaff %>% 
  names()
```

#### number of deaths
```{r}
titanic_staff_notstaff %>% 
  dplyr::filter(survived == "no") %>% 
  nrow()
```

#### number of deaths for those that are staff
```{r}
titanic_staff_notstaff %>% 
  dplyr::filter(survived == "no", class == "staff") %>% 
  nrow()
```

#### number of deaths for those who are passengers
```{r}
titanic_staff_notstaff %>% 
  dplyr::filter(survived == "no", class == "passenger") %>% 
  nrow()
```

#### So more passengers than staff did die, but how many out of each group did not die?

```{r}
titanic_staff_notstaff %>% 
  dplyr::filter(class == "passenger") %>% 
  nrow()
```
so out of 1317 passengers, 817 died and 500 survived

```{r}
titanic_staff_notstaff %>% 
  dplyr::filter(class == "staff") %>% 
  nrow()
```

so out of 890 staff, 817 died and 73 survived

#### likelihood of surviving
```{r}
titanic_staff <- titanic_staff_notstaff %>% 
  dplyr::filter(class == "staff")
titanic_passengers <- titanic_staff_notstaff %>% 
  dplyr::filter(class == "passenger")
```

staff
```{r}
titanic_staff %>% 
  dplyr::filter(survived == "yes") %>%
  dplyr::summarise(prob = n()/nrow(titanic_staff))
```
passengers
```{r}
titanic_passengers %>% 
  dplyr::filter(survived == "yes") %>%
  dplyr::summarise(prob = n()/nrow(titanic_passengers))
```
The probability of surviving is higher among passengers than staff.

## Extra questions

#### 1 
dice outcomes = 1,2,3,4,5,6
less than 5 = 1,2,3,4
4/6 = 2/3 = 0.6666666667

#### 2
```{r}
rolldie(3,6) %>% 
  nrow()
```

#### 3

##### i.
```{r}
four_die <- dplyr::as_tibble(rolldie(4, 6))

four_die<- four_die %>% 
  mutate(sum = X1 + X2 + X3 + X4)

four_die %>% 
  dplyr::filter(sum == 5:7) %>% 
  nrow()
```

##### ii
```{r}
four_die %>% 
  dplyr::filter(sum == 5:7) %>% 
  summarise(prob = n()/nrow(four_die))
```

##### iii
###### the assumption is that the size of the outcome counts the permutations instead of combinations

```{r}
people <- c(1, 2, 3, 4, 5)

chairs <- as_tibble(
  permutations(
    n = 5, 
    r = 5, 
    v = people, 
    repeats.allowed = FALSE
  )
)
```

###### the 'right' order would be 1,2,3,4,5 or 5,4,3,2,1. So to count the probability, the number of permutations has to be calculated.

```{r}
nrow(chairs)
```
The probability is
```{r}
2/120
```

