---
title: "Weekend Homework"
output: html_notebook
---

```{r}
library(tidyverse)
library(janitor)
library(naniar)

books_data <-read_delim("/Users/AbbyUtama/codeclan_work/week_01/day_5/weekend_homework/data/books.csv", delim = ",", 
                        locale = locale(encoding = "UTF-8",
                        date_format = '%d/%m/%Y'))
                        
cols(authors = col_character(),
     average_rating = col_double(),
     isbn = col_double(),
     isbn13 = col_double(),
     language_code = col_character(),
     num_pages = col_double(),
     text_review_count = col_double(),
     publication_date = col_date(),
     publisher = col_character())

col_types = cols("isbn" = col_double() , "isbn13" = col_double())

books_data <- clean_names(books_data)
names(books_data)

```
***Viewing the data***
```{r}
dim(books_data)
```

```{r}
str(books_data)
```

***Changing ISBN and ISBN-13 to Numerical***

```{r}
books_data <- books_data %>% 
  select(book_id, title, authors, average_rating, isbn13, language_code, num_pages, ratings_count, text_reviews_count, publication_date, publisher) %>% 
  transform(isbn13 = as.numeric(isbn13))

books_data %>% 
  summarise(count=sum(is.na(isbn13)))
```

***Languages***

```{r}
books_data %>% 
  distinct(language_code)
```
Remove the different types of "Eng" and replace with "Eng"

```{r}
books_data <- books_data %>% 
  mutate(language_code = recode(language_code,
    "en-US" = "eng",
    "en-GB" = "eng",
    "en-CA" = "eng",
    "enm" = "eng"
  ))
```

See how many books are published in each language

```{r}
books_data %>% 
  group_by(language_code) %>% 
  summarise(length(book_id))
```

***Pages***

Changing 0 pages to NA

```{r}
books_data <- books_data %>% 
  mutate(num_pages, num_pages = na_if(num_pages, 0)) 

books_data %>% 
  summarise(count=sum(is.na(num_pages)))
```
Imputing the NA into the median number of pages
```{r}
imputed_books_data <- books_data %>% 
  mutate(num_pages = coalesce(num_pages, median(num_pages, na.rm = TRUE)))

imputed_books_data
```
***Ratings count and text reviews count***

```{r}
imputed_books_data <-imputed_books_data %>% 
  mutate(ratings_count, ratings_count = na_if(ratings_count, 0)) %>% 
  mutate(text_reviews_count, text_reviews_count = na_if(text_reviews_count, 0))

imputed_books_data <- imputed_books_data %>% 
  mutate(ratings_count = coalesce(ratings_count, median(ratings_count, na.rm = TRUE))) %>% 
  mutate(text_reviews_count = coalesce(text_reviews_count, median(text_reviews_count, na.rm = TRUE)))

imputed_books_data
```
***Number of ratings***

```{r}
imputed_books_data %>% 
  select(ratings_count) %>% 
  arrange(ratings_count) %>% 
  tail(1000)
```

Making groups of ratings based on how many times each book was rated
```{r}
ratings_by_group <- imputed_books_data %>% 
  mutate(ratings_count = case_when(
    ratings_count < 100 ~ "0-100 ratings",
    ratings_count < 1000 ~ "100-1000 ratings",
    ratings_count < 10000 ~ "1000-10,000 ratings",
    ratings_count < 50000 ~ "10,000 - 50,000 ratings",
    ratings_count < 100000 ~ "50,000 - 100,000 ratings",
    ratings_count < 500000 ~ "100,000 - 500,000 ratings",
    ratings_count < 1000000 ~ "500,000 - 1,000,000 ratings",
    ratings_count < 2000000 ~ "1,000,000 - 2,000,000 ratings",
    ratings_count > 2000000 ~ "2,000,000+ ratings"
  ))
```

Grouped into the number of ratings, and how many books are there in each group

```{r}
ratings_by_group %>% 
  group_by(ratings_count) %>% 
  summarise(number_of_books = length(book_id))
```

***Average rating per publisher***
```{r}
imputed_books_data %>% 
  distinct(publisher)
```
```{r}
imputed_books_data %>% 
  group_by(publisher) %>% 
  summarise(number_of_books = length(book_id))
```


Recode some publisher names


```{r}
imputed_books_data <- imputed_books_data %>% 
  mutate(publisher = recode(
    "ACE" = "Ace",
    "Addison Wesley" = "Addison Wesley Publishing Company",
    "Alfred A.Knopf" = "Alfred A. Knopf",
    "Amistad Press" = "Amistad Press",
    "Amherst Media  Inc." = "Amherst Media",
    "Atlantic" = "Atlantic Books",
    "Berkley" = "Berkley Books",
    "Scholastic Inc" = "Scholastic",
    "Back Bay Books" = "Back Bay",
    "Baen Books" = "Baen",
    "Ballantine" = "Ballantine",
    "BALLANTINE BOOKS" = "Ballantine",
    "Ballantine Books" = "Ballantine",
    "Bantam Fanfare" = "Bantam",
    "Bantam Doubleday Dell (NYC)" = "Bantam Doubleday Dell",
    "Bantam Doubleday Dell Publishing Company Inc" = "Bantam Doubleday Dell",
    .x = (publisher)
  ))
```


Impute average ratings
```{r}
imputed_ratings <- imputed_ratings %>% 
  mutate(average_rating = coalesce(average_rating, mean(average_rating, na.rm = TRUE)))
```


```{r}
imputed_ratings %>% 
  group_by(publisher) %>% 
 summarise((mean(average_rating, na.rm= TRUE)))

```

***Popularity of books***
```{r}
imputed_books_data <- imputed_books_data %>%
  mutate(popularity = text_reviews_count * average_rating)

imputed_books_data %>% 
  select(popularity)
  
```
Grouping the publishers by popularity
```{r}
imputed_books_data %>% 
  group_by(publisher) %>% 
  summarise(publisher, mean(popularity, na.rm=TRUE))
```

***Questions***

1. How to remove dates from character vectors????
2. How to move data from one column to the next???

