---
title: "Cancer incidence in the Borders"
author: "Abbygail Utama"
date: "12/16/2020"
output: html_document
---

```{r, include = FALSE}
library(tidyverse)
library(janitor)
library(plotly)
library(lubridate)
library(tsibble)

cancer_incidence <- read_csv("../clean_data/cancer_incidence_scotland.csv")

scotland <- read_csv("../clean_data/scotland_wide.csv")

borders <- cancer_incidence %>% 
  filter(health_board == "NHS Borders")

nationwide_cancer <- rbind(cancer_incidence, scotland)
```

# Scotland wide data

### Cancer incidence between sexes across Scotland

```{r}
ggplotly(nationwide_cancer %>% 
  filter(sex != "All",
         health_board == "scotland_wide",
         cancer_site == "All cancer types") %>% 
  ggplot()+
  aes(x = year, y = crude_rate, colour = sex)+
    labs(x = "Year", y = "Crude rate", title = "Cancer incidence between men and women")+
  geom_line())
```


### Cancer incidence by health board in Scotland


```{r}
ggplotly(nationwide_cancer %>% 
  filter(sex == "All",
         cancer_site == "All cancer types") %>% 
  ggplot()+
  aes(x = year, y = crude_rate, colour = health_board)+
    labs(x = "Year", y = "Crude rate", title = "Crude rate of all cancer types per health board")+
  geom_line()+
  theme_minimal())
```


### Top 5 cancer incidence by cancer type in the past 24 years

```{r}
ggplotly(nationwide_cancer %>% 
  filter(sex == "All",
         cancer_site != "All cancer types",
         health_board == "scotland_wide") %>% 
    group_by(year) %>% 
  slice_max(crude_rate, n = 3) %>% 
ggplot()+
  aes(x = year, y = crude_rate, fill = cancer_site)+
   theme(legend.position = "none")+
    labs(x = "Year", y = "Crude rate", title = "Top 5 highest incidences of cancer")+
  geom_col())
```


# Cancer incidence in the Borders compared to Scotland wide data

### Cancer incidence in the Borders compared to Scotland as a whole

```{r}
ggplotly(nationwide_cancer %>%
 filter(sex %in% "All",
        cancer_site == "All cancer types",
        health_board %in% c("scotland_wide", "NHS Borders")) %>%
 ggplot() +
 aes(x = year, y = crude_rate, colour = health_board) +
 geom_line(size = 1L) +
  geom_smooth(span = 0.75)+
  labs(x = "Year", y = "Crude rate", title = "Cancer incidence in the Borders compared to Scotland wide")+
 scale_color_hue() +
 theme_minimal())
```
### The top 5 highest incidences of cancer per health board over the years (1994 - 2018)

```{r}
nationwide_cancer %>% 
  filter(cancer_site == "All cancer types",
         sex == "All") %>% 
  group_by(year) %>% 
  slice_max(crude_rate, n = 5) %>% 
  select(year, health_board, crude_rate)
```
#### When this table is graphed, it is clear that NHS Borders is present in the top 5 21 out of the 24 years recorded

```{r}
nationwide_cancer %>% 
  filter(cancer_site == "All cancer types",
         sex == "All") %>% 
  group_by(year) %>% 
  slice_max(crude_rate, n = 5) %>% 
  ggplot()+
  aes(x = year, y = crude_rate, fill = (health_board == "NHS Borders"))+
  scale_fill_discrete(name = " ", labels = c("Other health boards", "NHS Borders"))+
  labs(x = "Year", y = "Crude rate", title = "Top 5 Health Boards with Highest Incidence of Cancer in Scotland")+
  geom_col()
```
# Cancer data in the Borders

### Breakdown of cancer incidence in the Borders by type of cancer, over time


```{r}
ggplotly(borders %>%
 filter(sex %in% "All",
        cancer_site != "All cancer types") %>%
 ggplot() +
 aes(x = year, y = crude_rate, colour = cancer_site) +
 geom_line(size = 1L) +
 scale_color_hue() +
   labs(x = "Year", y = "Crude rate", title = "Cancer incidence in the Borders", fill = "Type of cancer")+
 theme(legend.position = "none"))
```

```{r, warning = FALSE}
ggplotly(borders %>% 
  filter(sex != "All",
         cancer_site != "All cancer types") %>% 
    group_by(year, sex) %>% 
  slice_max(crude_rate, n = 3) %>% 
  ggplot()+
  aes(x = year, y = crude_rate, colour = cancer_site)+
  facet_wrap(~ sex)+
   theme(legend.position = "none")+
    labs(x = "Year", y = "Crude rate", title = "Top 3 highest incidences of cancer for men and women over the years")+
  geom_line()+
    geom_point())
```


