---
title: "Read me homework file"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "R Homework"
output: html_notebook
---
# My homework

**loading the data**

```{r}
library(tidyverse)

library(janitor)

library(assertr)
```

```{r}
meteor_data <- read_csv("meteorite_landings.csv")
```
```{r}
str(meteor_data)
```



```{r}
meteor_data
```


## Cleaning names using the clean_names function on the Janitor package
```{r}
meteor_data <- clean_names(meteor_data)
```

***changing the values to lowercase using str_to_lower function***
```{r}
meteor_data <- meteor_data %>% 
  mutate(name = str_to_lower(name))

meteor_data <- meteor_data %>% 
  mutate( fall = str_to_lower(fall))

meteor_data
```
## Separate latitude and longtitude

# I use the separate function so that latitude goes in one column and longtitude goes on the next

```{r}
meteor_data_wider <- meteor_data %>% 
  separate(geo_location, into = c("latitude", "longtitude"), sep = ",")

meteor_data_wider
```
***Removing unneccessary information i.e. the parantheses ***

```{r}
meteor_data_wider <- meteor_data_wider %>% 
  mutate(latitude = str_remove(latitude, pattern = "\\("))

meteor_data_wider <- meteor_data_wider %>% 
  mutate(longtitude = str_remove(longtitude, pattern = "\\)"))

meteor_data_wider
```
***Setting values as numeric***

```{r}
meteor_data_wider <- meteor_data_wider %>% 
  mutate(latitude = as.numeric(latitude))

meteor_data_wider <- meteor_data_wider %>% 
  mutate(longtitude = as.numeric(longtitude))

meteor_data_wider
```
## Removing NA in longtitude and latitude with 0

***using if_else function to set any NA or missing values to "0"***
```{r}
meteor_data_wider <- meteor_data_wider %>% 
  mutate(latitude = if_else(is.na(latitude), 0, (latitude)))

meteor_data_wider
```
***how many NA's are there after removing them?***

```{r}
meteor_data_wider %>% 
  count(is.na(latitude))
```
***Doing the same to longtitude***
```{r}
meteor_data_wider <- meteor_data_wider %>% 
  mutate(longtitude = if_else(is.na(longtitude), 0, (longtitude)))

meteor_data_wider
```
***How many NA's are there left?***

```{r}
meteor_data_wider %>% 
  count(is.na(longtitude))
```


## Removing values less than 1000g
```{r}
meteor_data_heavy <- meteor_data_wider %>% 
  filter(mass_g >= 1000)
```


```{r}
meteor_data_heavy %>% 
  slice_min(mass_g, n = 10, with_ties = TRUE)
```
## Ordering the data by year of discovery - from earliest to latest

```{r}
meteor_data_heavy <- meteor_data_heavy %>% 
  arrange(year)

meteor_data_heavy
```
## Bit of assertive programming

***Let's verify the longtitude and latitude are correct***
```{r}
meteor_data_heavy %>% 
  verify(latitude >= -90 & latitude <= 90) %>% 
  verify(longtitude >= -180 & longtitude <= 180) 
```
***No error, longtitude and latitude values were correct***

## The 10 largest meteorites
 
 ***The 10 heaviest meteorites***
```{r}
meteor_data_heavy %>% 
  arrange(desc(mass_g)) %>% 
  summarise(name, mass_g, year) %>% 
  head(10)
```
***let's convert the masses into tonnes***
```{r}
meteor_data_heavy <- meteor_data_heavy %>% 
  mutate(mass_g = sum(mass_g/1000000))
```


```{r}
meteor_data_heavy<- meteor_data_heavy %>% 
  rename(mass_tonnes = mass_g)
meteor_data_heavy
```
***let's look at the 10 heaviest meteors again***

```{r}
meteor_data_heavy %>% 
  arrange(desc(mass_tonnes)) %>% 
  summarise(name, mass_tonnes, year) %>% 
  head(10)
```
## The average mass of meteorites for those that fell vs those that were found

```{r}
meteor_data_wider %>%
  group_by(fall) %>% 
  summarise(avg_mass = mean(mass_g, na.rm = TRUE))
```


## The average number of meteorites each year for every year since 2000!
```{r}
meteor_data_wider %>% 
  filter(year >= 2000) %>% 
  group_by(year) %>% 
   summarise(number_that_fell = sum(length(id)))
```
***there seems to be something wrong, as one year is counted as 2101***

```{r}
meteor_data_wider %>% 
  filter(year >=2000) %>% 
  arrange(desc(year))
```
***I'll just check the ids to figure out what happened***
```{r}
meteor_data_wider %>% 
  filter(id == 57149)
```
```{r}
meteor_data_wider %>% 
  filter(id == 57151)
```
***This meteor seems to be between 2011 and 2012, I will just assume it was in 2011 as '2101' seems to be a typo of that year***


```{r}
meteor_data_wider <-meteor_data_wider %>% 
  mutate(year = str_replace(year, pattern = "2101", "2011"))

meteor_data_wider %>% 
  arrange(desc(year))
```
***no more years in 2101!***

# Let's run the previous chunk again
```{r}
meteor_data_wider %>% 
  filter(year >= 2000) %>% 
  group_by(year) %>% 
   summarise(number_that_fell = sum(length(id)))
```



### Extension!

## Imputing the mass -- meteorites probably don't weight 0g

***Let's look at the data***

```{r}
meteor_data_wider %>% 
  arrange(mass_g)
```
***Keeping in min that 'gove' and 'miller range 090478' are examples of meteorites with allegedly no mass**

```{r}
meteor_data_imputed <- meteor_data_wider %>% 
  mutate(mass_g = na_if(mass_g, 0)) %>% 
  mutate(mass_g = coalesce(mass_g, mean(mass_g, na.rm = TRUE)))

meteor_data_imputed
```
```{r}
meteor_data_imputed %>% 
  filter(name == "gove")
```
***gove is no longer weighing 0g, but let's assume it is an average sized meteor***

### Extension!

## Imputing the mass -- meteorites probably don't weight 0g

***Let's look at the data***
```{r}
meteor_data_wider %>% 
  arrange(mass_g)
```

**Keeping in min that 'gove' and 'miller range 090478' are examples of meteorites with allegedly no mass**

```{r}
meteor_data_imputed <- meteor_data_wider %>% 
  mutate(mass_g = na_if(mass_g, 0)) %>% 
  mutate(mass_g = coalesce(mass_g, mean(mass_g, na.rm = TRUE)))

meteor_data_imputed
```

```{r}
meteor_data_imputed %>% 
  filter(name == "gove")
```

***gove is no longer weighing 0g, so let's assume it is an average sized meteor***


