---
title: "R Homework"
output: html_notebook
---
#My homework

**loading the data**

```{r}
library(tidyverse)

library(janitor)

library(assertr)
```

```{r}
meteor_data <- read_csv("meteorite_landings.csv")
```
```{r}
str(meteor_data)
```

```{r}
meteor_data
```
##Cleaning names
```{r}
meteor_data <- clean_names(meteor_data)
```
```{r}
meteor_data <- meteor_data %>% 
  mutate(name = str_to_lower(name))

meteor_data <- meteor_data %>% 
  mutate( fall = str_to_lower(fall))

meteor_data
```
##Separate names 

```{r}
meteor_data_wider <- meteor_data %>% 
  separate(geo_location, into = c("latitude", "longtitude"), sep = ",")

meteor_data_wider
```
***Removing unneccessary information***

```{r}
meteor_data_wider <- meteor_data_wider %>% 
  mutate(latitude = str_remove(latitude, pattern = "\\("))

meteor_data_wider <- meteor_data_wider %>% 
  mutate(longtitude = str_remove(longtitude, pattern = "\\)"))

meteor_data_wider
```
***Setting values as numeric***

```{r}
meteor_data_wider <- meteor_data_wider %>% 
  mutate(latitude = as.numeric(latitude))

meteor_data_wider <- meteor_data_wider %>% 
  mutate(longtitude = as.numeric(longtitude))

meteor_data_wider
```
##Removing NA in longtitude and latitude with 0

```{r}
meteor_data_wider <- meteor_data_wider %>% 
  mutate(latitude = if_else(is.na(latitude), 0, (latitude)))

meteor_data_wider

meteor_data_wider %>% 
  count(is.na(latitude))
```
```{r}
meteor_data_wider <- meteor_data_wider %>% 
  mutate(longtitude = if_else(is.na(longtitude), 0, (longtitude)))

meteor_data_wider

meteor_data_wider %>% 
  count(is.na(longtitude))
```
##Removing values less than 1000g
```{r}
meteor_data_heavy <- meteor_data_wider %>% 
  filter(mass_g >= 1000)

meteor_data_heavy
```
##Ordering the data by year of discovery - from earliest to latest

```{r}
meteor_data_heavy <- meteor_data_heavy %>% 
  arrange(year)

meteor_data_heavy
```
##Bit of assertive programming

***Let's verify the longtitude and latitude are correct***
```{r}
meteor_data_heavy %>% 
  verify(latitude >= -90 & latitude <= 90) %>% 
  verify(longtitude >= -180 & longtitude <= 180) 
```
***No error, longtitude and latitude values were correct***

##10 heaviest meteorites

```{r}
meteor_data_heavy <- meteor_data_heavy %>% 
  mutate(mass_g = sum(mass_g/1000000))

meteor_data_heavy <-meteor_data_heavy %>%
 rename(mass_tonnes = mass_g)

meteor_data_heavy
```
##Average mass of meteorites

```{r}
meteor_data_wider %>%
  group_by(fall) %>% 
  summarise(avg_mass = mean(mass_g, na.rm = TRUE))
```


##Average number of meteorites each year
```{r}
meteor_data_wider %>% 
  filter(year >= 2000) %>% 
  group_by(year) %>% 
   summarise(number_that_fell = sum(length(id)))
```

