---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```
#### 1. 

```{r}
backpack <- CodeClanData::backpack

str(backpack)
```
#### 2.

```{r}
ggplot(backpack) +
  aes(x = backpack_weight) +
  geom_histogram()
```
The histogram shows the spread of the number of students carrying different backpack weights. It shows a clear curve where more students carry backpacks weighing approximately the median weight. Most students carry a 10 pound backpack.

#### 3.

```{r}
ggplot(backpack) +
  aes(x = backpack_weight, fill = sex) +
  geom_histogram(position = "dodge")
```
The histogram shows that girls tend to carry lighter backpacks, the heaviest backpack carried weighed 25 pounds for a girl, and 35 pounds for a boy.

#### 4.

```{r}
ggplot(backpack)+
  aes(x = body_weight, y = backpack_weight)+
  geom_point()+
  scale_x_log10()
```
There seems to be some correlation between increasing body weight and increasing backpack weight, however the values that correspond to body weight values of more than 200 pounds has a much weaker correlation.


#### 5.
```{r}
ggplot(backpack)+
  aes(x = body_weight, y = backpack_weight)+
  geom_point()+
  facet_wrap(~sex)+
  geom_smooth(method = "lm", se = FALSE)
```
The correlation between body weight and backpack weight is quite weak for women, but there seems to be no correlation between body weight and backpack weight for men.

#### 6.

```{r}
backpack <- backpack %>% 
  mutate(back_problems = factor(back_problems, levels = c("1", "0")))
```


```{r}
ggplot(backpack)+
  aes(x = "", y = "backpack_probkems",  fill = back_problems) +
  geom_bar(stat = "identity", width = 1)+
  coord_polar("y", start = 0)
  
```
There is clearly a larger proportion of people without back problems than the ones who do, though I can't seem to put labels on the pie chart and identify the exact percentage.

####7.

```{r}

```

I don't completely understand this question -- and it's really late already so i'm going to bed.


