---
title: "R Notebook"
output: html_notebook
---
```{r}
library(tidyverse)
library(janitor)
```
## MVP

```{r}
ames <- read_csv(here::here("data/ames.csv")) %>% 
  clean_names()
```
### Investigate the distribution of lot_area

```{r}
ames %>% 
  select(lot_area) %>% 
  glimpse()
```

```{r}
ames %>% 
  select(lot_area) %>% 
  ggplot()+
  aes(x = lot_area)+
  geom_histogram(aes(y = ..density..))
```
#### distribution is very right skewed

### Compute and visualise a bootstrap sampling distribution for the mean(lot_area) of the sold houses.
```{r}
library(infer)
```


```{r}
bootstrap_sample <- ames %>% 
  select(lot_area) %>% 
  rep_sample_n(size = 100, replace = TRUE, reps = 1000) %>% 
  summarise(mean_lot = mean(lot_area))
```


### Use your bootstrap distribution to calculate a 95% CI for mean(lot_area), and visualise it on the distribution
 


```{r}
infer_sample <- ames %>% 
  specify(response = lot_area) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "mean")

infer_95 <- infer_sample %>% 
  get_ci(level = 0.95, type = "percentile")

infer_sample %>% 
  visualise()+
  shade_ci(endpoints = infer_95)
```
### You would like to know the mean(lot_area) of the sold houses with higher confidence. Calculate the 99% CI for this variable (you can re-use your bootstrap distribution from above). Is it narrower or broader than the 95% CI? Does that make sense?

```{r}
infer_99 <- infer_sample %>% 
  get_ci(level = 0.99, type = "percentile")

infer_sample %>% 
  visualise()+
  shade_ci(endpoints = infer_99)
```
### Calculate the point estimate of the mean(lot_area)

```{r}
ci_95 <- bootstrap_sample %>% 
  summarise(
    mean = mean(mean_lot),
    lower = quantile(mean_lot, probs = 0.025),
upper = quantile(mean_lot, probs = 0.975)
  )

ci_95
```